Forecasting 2024 US election using linear regression

### 2024-10-27 paper/paper.qmd
updated paper in appendix and reference

@@

# Appendix

## Emerson College Polling Methodology

For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll. Survey Overview: The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S. presidential election. This appendix provides an in-depth analysis of their polling methodology, including the population, sample frame, recruitment process, and key strengths and weaknesses of their approach.

Methodology 1. Population, Frame, and Sample:\
Target Population: The target population for this poll includes U.S. citizens who are eligible to vote in the 2024 presidential election. Sample Frame: The sample consists of likely voters across the United States. Emerson College Polling uses voter registration databases to develop a sampling frame of registered voters, ensuring they capture individuals who are most likely to vote in the upcoming election. Sample Size: For this particular poll, 1,000 likely voters were surveyed. This sample size provides a margin of error of approximately ±3 percentage points, allowing for reasonable confidence in the poll's accuracy.

2.  Sample Recruitment:\
    Recruitment Method: Emerson College employs a multi-mode recruitment approach, including online, phone (landline and mobile), and SMS text outreach. Phone Interviews: Live interviewers call both landlines and mobile phones using random digit dialing (RDD) to ensure they capture respondents without internet access. Online Panels: Emerson also recruits respondents through online panels, using email invitations to individuals who match their demographic quotas. SMS Text Polling: In recent years, Emerson has increasingly used SMS text polling, allowing respondents to complete the survey via mobile devices.

Trade-offs of Recruitment Method:\
Strengths: The multi-mode approach ensures better coverage of different demographic groups, including older adults and those less likely to engage with online surveys. Weaknesses: The RDD approach can lead to lower response rates, especially with the increasing number of people avoiding unsolicited calls. The online component also introduces self-selection bias, where more politically engaged individuals may be overrepresented.

3.  Sampling Approach and Trade-offs:\
    Quota-based Sampling: Emerson uses quota sampling to ensure that the sample is representative of key demographics, including age, gender, race, and region. The quotas are based on U.S. Census data to maintain demographic diversity. Weighting: After data collection, Emerson applies post-stratification weighting to adjust for any imbalances in the sample, aligning it with population benchmarks. Trade-offs: While quota sampling ensures demographic diversity, it can introduce bias if certain groups are harder to reach or more likely to refuse participation (non-response bias). Weighting helps mitigate this issue but relies on accurate population benchmarks, which may not always reflect the electorate’s behavior accurately.

4.  Non-response Handling:\
    Non-response Bias: To minimize non-response bias, Emerson College Polling uses a combination of call-backs and reminder emails for online respondents. Additionally, post-survey weighting accounts for non-response patterns across key demographic groups. Adjustments for Non-response: Emerson uses statistical weighting to adjust the final results based on the response rate within each demographic group (e.g., age, gender, and race). This helps to reduce the skew in the data caused by differential response rates.

5.  Questionnaire Design:\
    Strengths: The survey is concise, focusing on core topics like voter intention, candidate preference, and key issues such as the economy and healthcare. This increases the likelihood that respondents complete the survey accurately and without fatigue. Emerson regularly tests its questionnaire to ensure clarity and avoid ambiguous questions, improving the reliability of the responses. Weaknesses: Binary Choice Bias: Some sections of the questionnaire force a binary choice between two candidates, which may oversimplify the respondents' true preferences, especially in a race with multiple candidates or undecided voters. Social Desirability Bias: Like most political polls, respondents may answer questions in a way they believe is socially acceptable, especially in terms of voter turnout or support for controversial candidates. This could lead to over-reporting of voter intention. Summary of Strengths and Weaknesses Strengths:

Multi-mode Surveying: Emerson’s use of phone, online, and SMS recruitment allows them to reach a broader cross-section of the population, minimizing the biases introduced by any one method. Post-stratification Weighting: The weighting process ensures the sample reflects the U.S. population, improving the reliability of the poll results. Timely Polling: The frequent release of polling data makes it possible to track shifts in voter sentiment over time. Weaknesses:

Potential for Non-response Bias: Despite efforts to mitigate it, non-response remains a concern, particularly among certain voter demographics who may be harder to reach through phone or online surveys. Self-selection Bias in Online Surveys: The online component may disproportionately attract respondents who are more politically engaged, which could skew results. By employing a multi-mode approach and adjusting for demographic imbalances through weighting, Emerson College Polling provides robust and timely data. However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​

## Idealized Methodology for US Presidential Election Forecast

This appendix outlines the methodology and design for conducting a U.S. presidential election forecast survey with a budget of \$100,000. The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.\

### Sampling Approach

To ensure a representative sample of likely voters, I will use a Composite Measure sampling method based on the past voter turnout data from the U.S. previous 2020 elections.After decising the sampling size in each state, I will use a stratified sampling bases on demographics,dividing population into subgroups, and a random sample is taken from each subgroup. We employ composite Measure sampling method refer from (), that increased our chances of selecting respondents from voters in states/ regions that have historically higher voter engagement as compared to the natural distribution we’d expect from the general population. While some states may have larger populations, we are interested in adjusting the sampling to reflect higher turnout rates. To better explain this composite measure of size, lets consider that we have two states that have similar population. For example, even though State A and State B may have similar populations, if State B consistently has a higher voter turnout in past elections, we want to increase the proportion of polls we conduct in State B. State A has a population of 1 million eligible voters, with a historical turnout rate of 50%. State B has a population of 1 million eligible voters, but its turnout rate is 70%. In a purely population-based sampling approach, each state would have an equal chance of being selected for polls: 50% for State A and 50% for State B. However, based on voter turnout, we modify these probabilities to increase the chance of selecting State B, since its voter turnout is historically higher.\
In following steps, we will explore how to use **voter turnout** as a key factor to create a **composite measure of size** for sampling US election polls. Instead of using population size alone, we adjust the sample allocation based on historical voter turnout, ensuring regions with higher engagement are more heavily represented in our polling data.\

#### Step 1: Define the Sampling Data

@@

#### Step 2: Calculate Actual Voters

@@

#### Step 3: Calculate Composite Measure of Size

@@

#### Step 4: Allocate Sample Based on Turnout

@@

### Target Population

@@

### Sample frame

@@

### Sample

#### Sample Size:

@@

| **Region**    | **States**                                                                                                                                                 |
|----------------------|--------------------------------------------------|
| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |

@@

@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP). The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.

**Stratification Variables**: After determining the number of respondents to be sampled from each region, stratified sampling will be applied across key demographic categories such as age, gender, race/ethnicity, and education level. This approach helps ensure that the final sample accurately reflects the diversity of the U.S. voting population by proportionally representing each subgroup within each region. To address potential non-response bias, post-stratification weighting[^1] will be applied, adjusting for any imbalances caused by differences in response rates across demographic groups. The sample will be stratified across several key demographic and geographic variables to ensure proportional representation of the U.S. voting population. These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%). Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%). Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%). For each variable, U.S. Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population. Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.

[^1]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.

#### Recruitment of Respondents

@@

#### Respondent Validation

@@

### Poll Aggregation

@@

### Survey Design

@@

In our survey, several questions are adapted from the Emerson College Polling data [@emerson]. We also apply insights from @survey to minimize response biases. Common biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB). Our survey primarily focuses on strategies to reduce moderacy bias, extreme response bias, ordering bias, SDB, and acquiescence bias. \#### Defination of the bias

@@

### Solution to the bias in our survey

@@

### Budget Breakdown

@@

## U.S. Presidential Election Polls Survey

@@

For any questions or concerns regarding this survey, please contact:\
**Email:** diana.shen\@mail.utoronto.ca

>>>>

## Dataset and Graph Sketches

Sketches depicting both the desired dataset and the graphs generated in this analysis are available in the GitHub Repository `other/sketches`.

## Data Cleaning

The data cleaning process involved filtering data to just high-quality pollsters (i.e numeric_grade >= 3.0) and filter to just Harris (i.e. candidate_name == "Kamala Harris")

## Attribution Statement

This work is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/). You are free to share, copy, redistribute, remix, transform, and build upon the material for any purpose, even commercially, as long as you credit the original creation.

> "Title of the Work" by Author Name, licensed under CC BY 4.0.

@@

# The New York Times/Siena College Polling Methodology

This appendix provides a comprehensive overview of the methodology employed by the Siena College Polling Institute in conducting its surveys.Siena College is renowned for its methodologically rigorous approach to political polling, focusing on accurately capturing voter sentiment during elections. Siena College has conducted polls in three key states: Michigan, Wisconsin, and Ohio.

In this section, we will delve into the key components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and the sampling strategies used. We will also address how non-response is managed and evaluate the strengths and weaknesses of the questionnaire design. By exploring these elements, this appendix aims to clarify how Siena College ensures the reliability and validity of its polling results, contributing valuable insights to the understanding of voter behavior and election outcomes.

## Pollster Overview

Siena College Polling Institute is a prominent pollster known for its comprehensive and methodologically rigorous surveys. It specializes in political polling and is particularly recognized for its work in understanding voter sentiment during elections.

Established in 1980 at Siena College in New York's Capital District, the Siena College Research Institute (SCRI) conducts surveys at regional, state, and national levels on various topics, including business, economics, politics, voter behavior, social issues, academics, and history. The institute carries out both expert and public opinion polls.

Students from Siena and other colleges participate in every survey, gaining hands-on experience in fields such as political science, computing, communications, sociology, and psychology. SCRI also hires interns for special projects involving event planning, in-depth research, report writing, and analysis. The results of SCRI's surveys are featured in major regional and national publications, including The Wall Street Journal and The New York Times, as well as in academic journals, books, and encyclopedias, both in print and online. Their findings are regularly highlighted in local and national television and radio broadcasts. SCRI conducts the Siena New York Poll, a monthly survey that captures the opinions of registered voters across New York State on current political issues, along with the New York State Index of Consumer Sentiment, which offers a quarterly assessment of New Yorkers' spending intentions. SCRI adheres to the American Association of Public Opinion Research (AAPOR) Code of Professional Ethics and Practices. The institute is often commissioned to carry out surveys for various organizations, businesses, and local and state government agencies. [@aboutsiena]

## Population, Frame and sample

In essence, statistics is about collecting data and making informed conclusions, even though we can never access every piece of information.\
From @tellingstories, we defined three key terms as:\
Target population : The collection of all items about which we would like to speak. / The entire group about which we want to draw conclusions\
Sampling frame : A list of all the items from the target population that we could get data about.\
Sample : The items from the sampling frame that we get data about.\

The target population for Siena’s polls includes registered voters eligible to vote in Michigan, Wisconsin, and Ohio. The sampling frame consists of a comprehensive list of registered voters, which includes demographic information for each voter. This enables the pollsters to ensure an appropriate representation of voters across various parties, races, and regions [@poll]. The sample of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group. The sample for the poll totals 2,055 likely voters, with 688 from Michigan, 687 from Ohio, and 680 from Wisconsin, surveyed from September 21 to 26, 2024.\

## Sample Recruitment

Siena use phone poll to recruit sample. Telephone polling is a common method for gathering public opinion and assessing voter sentiment by contacting individuals via landlines and mobile phones. This approach uses live interviewers to enhance data quality, allowing for clarification and nuanced responses. By utilizing random digit dialing or national voter registration databases, researchers can ensure a representative sample across various demographics. Despite its effectiveness in reaching diverse audiences quickly, telephone polling must address potential biases, such as nonresponse and shifts in communication habits, to maintain the reliability of its findings.[^1]

[^1]: Phone polls, once considered the gold standard in survey research, now compete with methods like online panels and text messaging. Their advantages have diminished due to declining response rates, which increase costs and may affect representativeness, raising concerns about their future viability. However, they still effectively reach a random selection of voters quickly, as there is no national email database and postal mail can be slow. Other methods, such as recruiting panelists by mail, risk attracting only the most politically engaged individuals. Recent elections have shown that telephone polls, including The Times/Siena Poll, continue to perform well due to the reliability of voter registration files in balancing party representation.

According to @freqqa, the polls are conducted by live interviewers at call centers located in Florida, New York, South Carolina, Texas, and Virginia. The respondents are randomly selected from a national database of registered voters and are contacted via both landlines and cellphones.

Siena polls are conducted over the phone in both English and Spanish. For these polls, interviewers made nearly 260,000 calls to just over 140,000 voters. Overall, about 97 percent of respondents were contacted on a cellphone for these polls.

## Sampling Approach

Siena employs a response-rate-adjusted stratified sampling of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group. The New York Times selected the sample in multiple stages to address differences in telephone coverage, nonresponses, and notable variations in telephone number productivity by state.

Stratified sampling is typically utilized to ensure all strata of the population are represented. When considering our population, it typically consists of various groupings. These can range from a country being divided into states, provinces, counties, or statistical districts to a university comprising faculties and departments or even demographic characteristics groups among individuals. A stratified structure allows us to categorize the population into mutually exclusive and collectively exhaustive sub-populations known as "strata".

Stratification is employed to enhance sampling efficiency and ensure balance within the survey. For example, the population of the United States is approximately 335 million, with around 40 million residents in California and roughly half a million in Wyoming. In a survey with 10,000 responses, we would expect to receive only about 15 responses from Wyoming, which could complicate any inferences about that state. By implementing stratification, we could ensure, for instance, that there are 200 responses from each state. Within each state, we could then use random sampling to select individuals for data collection [@tellingstories].

In this scenario, we want to collect the polls from all strata of our target population to balance our poll result. The sample was stratified by political party, race, and region, and screened by M.S.G. to ensure that the cellular phone numbers were active. The Siena College Research Institute conducted the survey, with additional support from various institutions, including ReconMR, the Public Opinion Research Laboratory at the University of North Florida, the Institute for Policy and Opinion Research at Roanoke College, the Center for Public Opinion and Policy Research at Winthrop University in South Carolina, and the Survey Center at the University of New Hampshire. Interviewers sought to speak with the individuals listed on the voter file and would terminate the interview if those persons were unavailable. Overall, 97 percent of respondents across all four samples were reached via cellular phones.

The survey instrument was translated into Spanish by ReconMR, and bilingual interviewers began in English, following the respondent's preference for either language. Among self-reported Hispanics, 11 percent of interviews were conducted in Spanish, with this percentage rising to 15 percent in the weighted sample of registered voters. An interview was considered complete for inclusion in the voting questions if the respondent did not drop out after answering the two self-reported variables used for weighting—age and education—and responded to at least one question related to age, education, or presidential candidate preference.

Stratified sampling enhances the representativeness of the sample by ensuring that smaller subgroups, which might otherwise be underrepresented, are adequately included. A significant advantage of this method is that it allows for more efficient resource allocation, enabling researchers to target specific groups and gather more insightful data. However, this focus can lead to **higher overall costs**, particularly due to the comprehensive data collection and analysis required when sampling large states or countries. Additionally, while stratified sampling provides richer insights into the characteristics and opinions of different subgroups, it introduces **complexity in data analysis**, necessitating advanced statistical techniques to interpret the results accurately. Consequently, researchers must have sufficient evidence to determine how to weight each stratum appropriately. Lastly, if the strata are not well-defined or if there is an imbalance in sampling, it could still result in sampling bias. Overall, while stratified sampling offers substantial benefits in terms of representation and analytical depth, it also presents challenges related to complexity, cost, and potential bias if not executed carefully.

## Non-response Bias

An interview was deemed complete for inclusion in the voting preference questions if the respondent stayed engaged in the survey after answering the two self-reported variables used for weighting—age and education—and provided responses to at least one question concerning age, education, or the presidential election candidate reference. If these conditions were not met, the interview was recorded as a non-response.

To handle the non-response bias, Siena choose to use weighting adjustments. Weighting is like balancing a scale to make sure each group in the survey counts the right amount. It changes the importance of each answer depending on how likely people are to skip the survey [@surveylab].

Siena use several steps to address nonresponse bias and ensure the reliability of the results. The weighting process was conducted by The Times using the R survey package and involved multiple adjustments. Initially, the samples were adjusted for the unequal probability of selection by stratum. Subsequently, the first-stage weight was modified to account for the likelihood that a registrant would vote in the 2024 election, based on a model derived from turnout data in the 2020 election.

To create a composition that reflects the likely electorate, the sample was further weighted to match specific targets. These targets were developed by aggregating individual-level turnout estimates from the L2 voter file, with categories aligning with those used for registered voters. Additionally, the initial likely electorate weight was adjusted to incorporate self-reported voting intentions. In this final adjustment, four-fifths of the probability that a registrant would vote in the 2024 election was based on their ex ante modeled turnout score, while one-fifth relied on their self-reported intentions, adjusted for the tendency of survey respondents to have higher turnout rates than nonrespondents.

The final likely electorate weight was calculated by multiplying the modeled electorate rake weight by the final turnout probability and then dividing by the ex ante modeled turnout probability. This comprehensive approach to weighting helps mitigate nonresponse bias by ensuring that the sample reflects both the characteristics of the general population and the expected behavior of likely voters. As a result, the sample of respondents who completed all questions in the survey was adjusted to accurately represent the likely electorate, enhancing the overall validity of the findings.

## Questionnaire Design

**Strengths**:

The questionnaire is crafted to be concise and straightforward, effectively minimizing respondent fatigue and maximizing clarity in question phrasing. This design is essential for maintaining participant engagement, especially in surveys that may include a wide array of questions. Additionally, the use of a mix of closed and open-ended formats allows for a comprehensive analysis of voter sentiment. Closed-ended questions yield quantifiable data, enabling researchers to identify trends and patterns, while open-ended questions provide rich qualitative insights that contextualize these trends.

The careful structuring of questions also plays a crucial role in reducing moderacy bias, where respondents might lean towards neutral options when unsure. By providing clear response categories, the questionnaire encourages participants to express their opinions more decisively. Furthermore, the inclusion of diverse question types can mitigate acquiescence bias, which occurs when respondents habitually agree with statements instead of reflecting their true feelings. By framing questions in a balanced manner and avoiding leading language, the design helps ensure that participants feel comfortable expressing varied opinions.

**Weaknesses**:

However, the questionnaire is not without its weaknesses. Critics highlight that the reliance on agree-disagree formats can lead to acquiescence bias, where respondents might select favorable options rather than accurately expressing their true opinions. This tendency skews the results, potentially misrepresenting genuine voter sentiment and leading to misleading conclusions.

Moreover, the questionnaire may not adequately address the nuances that are important to specific demographic groups, resulting in potential gaps in understanding voter motivations. For instance, certain groups may have distinct issues or concerns that are not adequately captured by the survey's questions. This limitation can contribute to nonresponse bias, where individuals from underrepresented groups choose not to participate or drop out of the survey, further skewing the results.

Additionally, the structure of the questions could inadvertently create extreme response bias, where participants feel pressured to choose the most extreme options rather than selecting a moderate stance. This bias can be exacerbated by the order in which questions are presented. If respondents encounter highly charged or leading questions early in the survey, they may be influenced to respond similarly in subsequent questions, a phenomenon known as ordering bias.

Furthermore, while the questionnaire aims to be inclusive, if it fails to adequately represent the voices of certain demographic groups, it could lead to a lack of adequacy in the data collected. This inadequacy undermines the ability to draw comprehensive conclusions about the electorate, particularly in a diverse political landscape.

In summary, while the questionnaire design has strengths in clarity and mixed-format questions that encourage engagement and nuanced responses, it also faces challenges related to biases such as acquiescence, nonresponse, extreme response tendencies, and ordering effects. To enhance its effectiveness, future iterations of the questionnaire should strive to incorporate more varied question types, ensure demographic representation, and remain mindful of question order and phrasing to minimize the potential for bias and improve the overall validity of the findings.

# Idealized Methodology for US Presidential Election Forecast

This appendix details the methodology and design for conducting a U.S. presidential election forecast survey with a budget of \$100,000. The objective is to generate an accurate and reliable prediction of the election outcome while ensuring data quality through meticulous sampling, recruitment, validation, and aggregation of results.\

## Sampling Approach

To ensure a representative sample of likely voters, I will employ a Composite Measure sampling method based on past voter turnout data from the 2020 U.S. elections. After determining the sample size for each state, I will use stratified sampling based on demographics, dividing the population into subgroups and taking random samples from each subgroup. This Composite Measure sampling approach, as referenced in @india, enhances our chances of selecting respondents from states or regions that have historically exhibited higher voter engagement compared to the general population distribution. While some states may have larger populations, we aim to adjust the sampling to reflect higher turnout rates.

To illustrate this Composite Measure of size, consider two states with similar populations. For instance, although State A and State B both have 1 million eligible voters, State B consistently shows a higher voter turnout in past elections. Therefore, we will increase the proportion of polls conducted in State B. In this scenario, State A has a historical turnout rate of 50%, while State B has a turnout rate of 70%. In a purely population-based sampling approach, both states would have an equal chance of being selected for polls: 50% for State A and 50% for State B. However, by incorporating voter turnout, we modify these probabilities to increase the likelihood of selecting State B due to its higher historical turnout.

In the subsequent steps, we will detail how to utilize **voter turnout** as a crucial factor in creating a **composite measure of size** for sampling U.S. election polls. Rather than relying solely on population size, we will adjust the sample allocation based on historical voter turnout, ensuring that regions with higher engagement are more prominently represented in our polling data.

### Step 1: Define the Sampling Data

@@

### Step 2: Calculate Actual Voters

@@

### Step 3: Calculate Composite Measure of Size

@@

### Step 4: Allocate Sample Based on Turnout

@@

### Stratification Variables

After determining the number of respondents to be sampled from each region, stratified sampling will be employed across key demographic categories, including age, gender, race/ethnicity, and education level. This approach ensures that the final sample accurately reflects the diversity of the U.S. voting population by proportionally representing each subgroup within every region. To mitigate potential non-response bias, post-stratification weighting[^2] will be applied, correcting for any imbalances caused by variations in response rates among different demographic groups. The sample will be stratified based on several critical demographic and geographic variables to guarantee proportional representation of the U.S. voting population. Strata information will be sourced from U.S. census data obtained through IPUMS USA [@ruggles2024ipums].

These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%). Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%). Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%). For each variable, U.S. Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population. Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.

[^2]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.

## Target Population

@@

## Sample frame

@@

## Sample

@@

| **Region**    | **States**                                                                                                                                                 |
|------------------------|------------------------------------------------|
| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |

@@

@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wikivote], including voter turnout, total ballots cast, and Voting Eligible Population (VEP). The sample size for each region shown in @tbl-samplesize was determined based on the **Composite Measure Sampling Proportion**.

## Recruitment of Respondents

@@

## Handling Non-response bias

Nonresponse bias occurs when participants are unwilling or unable to respond to specific questions or complete the entire survey. For example, since our survey takes about 15 minutes to finish, there is a potential for nonresponse bias to arise. To address this concern, as highlighted by @surveymonkey, we strive to establish clear expectations regarding the survey's objectives and the estimated time required for completion. Furthermore, we utilize post-stratification, which changes the survey weights to make sure the group that answered fits well with the actual population characteristics [@surveylab].

## Respondent Validation

@@

## Poll Aggregation

@@

## Survey Design

@@

In our survey, several questions are adapted from the Emerson College Polling data [@emerson]. We apply insights from @survey to minimize response biases. Common response biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB). Our survey primarily focuses on strategies to reduce moderacy bias, extreme response bias, ordering bias, SDB, and acquiescence bias.

### Defination of the response bias

@@

### Solution to the response bias in our survey

@@

## Budget Breakdown

@@

## Copy of U.S. Presidential Election Polls Survey

@@

For any questions or concerns regarding this survey, please contact:\
**Email:**  diana.shen\@mail.utoronto.ca; jinyan.wei\@mail.utoronto.ca; huayan.yu\@mail.utoronto.ca
